\EVOSUITE at the SBST 2022 Tool Competition

### 2022-03-13 papers/sbst22/paper_sbst22.tex
Fix small typos

\EVOSUITE~\cite{FrA11c} automatically generates test suites for Java classes
using evolutionary search. As input \EVOSUITE only requires the name of the
target class as well as the classpath on which the compiled bytecode of the
target class as well as its dependencies are located. \EVOSUITE first extracts
information about the relevant classes as well as their constructors, methods,
and fields using a basic static analysis. It instruments the bytecode while
classes are loaded by the Java classloader, such that \EVOSUITE can produce
execution traces for test executions, and to avoid test flakiness by replacing
non-deterministic calls with deterministic, mocked versions. Finally, \EVOSUITE
applies meta-heuristic search algorithms to automatically produce JUnit test
cases aimed at maximising code coverage.
%Besides the basic command line interface there are also plugins for popular development environments such as IntelliJ, Eclipse, or Maven~\cite{ICST16_Tool}.

\EVOSUITE generates tests using evolutionary algorithms. 
%
For this, it uses a genetic encoding of test cases consisting of variable-length sequences of Java statements (e.g., primitive statements as well as calls on constructors or methods). Standard evolutionary search operators (e.g., selection, crossover, mutation) are adapted for this representation. 
%
\EVOSUITE provides several different evolutionary algorithms to operate on this
representation. The initial approach was to optimise entire test suites with
respect to their overall code coverage~\cite{GoA_TSE12}. However, after
extensive evaluation~\cite{ea_evaluation} the default is now the
\textit{Dynamic Many-Objective Sorting Algorithm} (DynaMOSA) search
algorithm~\cite{dynamosa}, which operates at the test case level.
%
The search is driven by fitness functions that encode coverage criteria. \EVOSUITE can optimise for several criteria simultaneously, and the core fitness functions in \EVOSUITE are based on traditional heuristics for code coverage, such as the branch distance and the approach level (see~\cite{GoA_TSE12} for more details). However, there are several further fitness functions based on mutation testing~\cite{emse14_mutation} as well as other basic criteria~\cite{rojas2015combining}.

A large share of the complexity of \EVOSUITE's code base is due to efforts to
avoid flakiness in the generated tests. One the one hand, this covers extensive
instrumentation and mocking. On the other hand, \EVOSUITE also compiles and
executes each test individually to avoid compilation errors (which may be the
result of bugs in \EVOSUITE) or flakiness caused by non-determinism in the
class under test.

>>>>

\EVOSUITE~\cite{FrA11c} automatically generates test suites for Java classes
using evolutionary search. As input \EVOSUITE only requires the name of the
target class as well as the classpath on which the compiled bytecode of the
target class and its dependencies are located. \EVOSUITE first extracts
information about the relevant classes as well as their constructors, methods,
and fields using a basic static analysis. It instruments the bytecode while
classes are loaded by the Java classloader, such that \EVOSUITE can produce
execution traces for test executions, and to avoid test flakiness by replacing
non-deterministic calls with deterministic, mocked versions. Finally, \EVOSUITE
applies meta-heuristic search algorithms to automatically produce JUnit test
cases aimed at maximising code coverage.
%Besides the basic command line interface there are also plugins for popular development environments such as IntelliJ, Eclipse, or Maven~\cite{ICST16_Tool}.

\EVOSUITE generates tests using evolutionary algorithms. 
%
For this, it uses a genetic encoding of test cases consisting of variable-length sequences of Java statements (e.g., primitive statements as well as calls on constructors or methods). Standard evolutionary search operators (e.g., selection, crossover, mutation) are adapted for this representation. 
%
\EVOSUITE provides several different evolutionary algorithms to operate on this
representation. The initial approach was to optimise entire test suites with
respect to their overall code coverage~\cite{GoA_TSE12}. However, after
extensive evaluation~\cite{ea_evaluation} the default is now the
\emph{Dynamic Many-Objective Sorting Algorithm} (DynaMOSA) search
algorithm~\cite{dynamosa}, which operates at the test case level.
%
The search is driven by fitness functions that encode coverage criteria. \EVOSUITE can optimise for several criteria simultaneously, and the core fitness functions in \EVOSUITE are based on traditional heuristics for code coverage, such as the branch distance and the approach level (see~\cite{GoA_TSE12} for more details). However, there are several further fitness functions based on mutation testing~\cite{emse14_mutation} as well as other basic criteria~\cite{rojas2015combining}.

A large share of the complexity of \EVOSUITE's code base is due to efforts to
avoid flakiness in the generated tests. On the one hand, this covers extensive
instrumentation and mocking. On the other hand, \EVOSUITE also compiles and
executes each test individually to avoid compilation errors (which may be the
result of bugs in \EVOSUITE) or flakiness caused by non-determinism in the
class under test.
